Reanalysis Step 2: Multiple Imputation

### 2025-08-29 reanalysis-2-multiple_imputation.qmd
bugfix

  # Fellow eye predictors (if available)
  "fellow_baseline_VA",
  "fellow_intermediate_VA",
  "fellow_outcome_VA",
  "fellow_lapsed",
  "fellow_dr",
  "n_eyes",
  "has_fellow",
  "patient_worst_baseline",
  "patient_best_baseline",
  "patient_ever_lapsed"
)

@@

# Expected warnings about collinearity:
# 1. e_mrn_deidentified: Constant (patient ID) - expected, not used as predictor
# 2. outcome_VA_logMAR & fellow_outcome_VA: Identical missingness patterns (both NA for excluded cohort)
#    This is expected and OK - they're measuring different eyes but missing for same reason
# 3. Variables removed to avoid true collinearity: has_fellow, patient_ever_lapsed, fellow_lapsed
#    These were redundant with other variables in the model

>>>>

  # Fellow eye predictors (if available)
  "fellow_baseline_VA",
  "fellow_intermediate_VA",
  "fellow_outcome_VA",
  # "fellow_lapsed",  # REMOVED: Collinear with ever_lapse_binary
  "fellow_dr",
  "n_eyes",
  # "has_fellow",  # REMOVED: Perfectly collinear with n_eyes (has_fellow = n_eyes == 2)
  "patient_worst_baseline",
  "patient_best_baseline"
  # "patient_ever_lapsed"  # REMOVED: Collinear with ever_lapse_binary
)

@@

# Expected warnings about collinearity:
# 1. e_mrn_deidentified: Constant (patient ID) - expected, not used as predictor
# 2. outcome_VA_logMAR & fellow_outcome_VA: Identical missingness patterns (both NA for excluded cohort)
#    This is EXPECTED and HARMLESS - they measure different eyes but are missing for same structural reason
#    MICE will drop fellow_outcome_VA from the imputation model for outcome_VA_logMAR to avoid
#    singularity, but it can still be used to predict other variables. This does NOT affect results.
# 
# Variables removed to avoid true collinearity: has_fellow, patient_ever_lapsed, fellow_lapsed
